---
output: github_document
editor_options: 
  chunk_output_type: console
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE,
          fig.width = 5,
          fig.height = 3,
          out.width = "75%",
          fig.align = "center")
options(list(dplyr.summarise.inform = FALSE))
theme_set( theme_classic() )

library( CSM )
```


<!-- badges: start -->
<!-- badges: end -->



# Synthetic Caliper Matching (scmatch2)

This package implements the Synthetic Caliper Matching approach, which is a blend of radius matching using distance metrics put on the covariate distribution itself, and the synthetic control method.
In particular, it identifies sets of units local to each treated unit in turn, and then makes a synthetic control for each treated unit using those local units.

The GitHub repo also has replication materials for the associated paper in the `scripts` directory; see below for further discussion of this added-on code.  The installed package will ignore `scripts`.

## Installation

You can install the development version of CSM from [GitHub](https://github.com/) with:

```
# install.packages("devtools")  # (if needed)
devtools::install_github("jche/scmatch2")
```


# Quick demo of package 

We generate a small toy dataset to illustrate the main methods of interest:

```{r}
set.seed( 4044440 )
dat <- gen_one_toy(nt = 5)
dat
ggplot( dat, aes( X1, X2, color = Z ) ) + geom_point() +
  coord_fixed()
```

To calculate matches, call `get_cal_matches()`--it will match, make synthetic controls for each unit, and give you a final dataset back, stored as an `csm_matches` object:
```{r}
mtch <- get_cal_matches( dat, 
                        metric = "maximum",
                        scaling = c( 1/0.2, 1/0.2),
                        caliper = 1, 
                        rad_method = "adaptive", 
                        est_method = "scm" ) 
mtch
```

There are a variety of things you can pull from the result object.
You can get a list of statistics on the treated units:
```{r}
mtch$treatment_table
```

You can see all the units used, grouped by subclass:
```{r}
full_unit_table(mtch, nonzero_weight_only = TRUE ) 
```

You can get the final dataset (here filtering to only matches within the initial caliper):
```{r}
result_table( mtch, feasible_only = TRUE )
```

You can also get the final generated result as a data.frame by casting the result into a dataframe:
```{r}
head( as.data.frame( mtch ), n = 10 )
```

You can estimate impacts on the matched dataset using whatever tools you want, or use the options discussed in our paper as so:
```{r}
get_ATT_estimate( mtch )
```


# Dependencies

This package has some tricky dependencies.
In particular, it (optionally) uses a DGP (for simulation) from ACIC 2016:

```
remotes::install_github("vdorie/aciccomp/2016")
```
You should not need this package unless generating synthetic data.



# TO DO List

- Move the wrappers file to the scripts/simulation folder (it is utilities for simulation, not core package stuff) 
- Keep boot_CSM (and the utility functions it uses), but move the other bootstrap stuff out of the main package.
- Make a separate folder for the inference simulation and it should have the annalysis file and the simulation file in it.


# Notes on scripts directory

The scripts directory includes the simulations of the paper and a variety of illustrations that support the paper.  They use the package, but are not the package.

In the scripts directory are several folders:

 - analysis: This has the paper results.  This makes plots and tables out of the simulation results.
 - datagen: DGPs for demonstration.  The simulation DGPs are in the sim_data.R file in the main package.
 - demo: Illustrates use of the package.
 - ferman-data-analysis: Empirical example in paper
 - figs: Similar role as analysis, making figures out of existing results
 - sims: Code that runs the various simulations in the paper

TODO: Reorg the directory structure a bit:

Thing we want:

 - figs: Makes the illustration figures from the main paper, but nothing else.  (No empirical or simulation results in this folder.)
 - empirical: Does the empirical analysis (both Ferman data and LaLonde data analysis files)
 - demo: Illustrates use of the package (only).  Not anything included in the main paper.
 - sims: The code to run the simulations
 - sim_analysis: The code to analyze the simulation results
 - sim_inference: The simulation and analysis code for the simulations evaluating inference.
 - datagen: Move this folder to old code, unless it is used by something else?


