---
output: github_document
editor_options: 
  chunk_output_type: console
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE,
          fig.width = 5,
          fig.height = 3,
          out.width = "75%",
          fig.align = "center")
options(list(dplyr.summarise.inform = FALSE))
theme_set( theme_classic() )

library( CSM )
```


<!-- badges: start -->
<!-- badges: end -->



# Caliper Synthetic Matching (scmatch2)

This package implements the Caliper Synthetic Matching approach, which is a blend of radius matching using distance metrics put on the covariate distribution itself, and the synthetic control method.
In particular, it identifies sets of units local to each treated unit in turn, and then makes a synthetic control for each treated unit using those local units.

Details can be found on the paper: [Che et. al. (2024), Caliper Synthetic Matching](https://arxiv.org/abs/2411.05246)

The GitHub repo also has replication materials for the associated paper in the `scripts` directory; see below for further discussion of this added-on code.  The installed package will ignore `scripts`.


## Installation

You can install the development version of CSM from [GitHub](https://github.com/) with:

```
# install.packages("devtools")  # (if needed)
devtools::install_github("jche/scmatch2")
```


# Quick demo of package 

We generate a small toy dataset to illustrate the main methods of interest:

```{r}
set.seed( 4044440 )
dat <- gen_one_toy(nt = 5)
dat
ggplot( dat, aes( X1, X2, color = Z ) ) + geom_point() +
  coord_fixed()
```

To calculate matches, call `get_cal_matches()`--it will match, make synthetic controls for each unit, and give you a final dataset back, stored as an `csm_matches` object:
```{r}
mtch <- get_cal_matches( dat, 
                         covs = ~ X1 + X2,
                         metric = "maximum",
                         scaling = c( 1/0.2, 1/0.2 ),
                         caliper = 1, 
                         rad_method = "adaptive", 
                         est_method = "scm" ) 
mtch
```

There are a variety of things you can pull from the result object.
You can get a list of statistics on the treated units:
```{r}
mtch$treatment_table
```

You can see all the units used, grouped by subclass:
```{r}
full_unit_table(mtch, nonzero_weight_only = TRUE ) 
```

You can get the final dataset (here filtering to only matches within the initial caliper):
```{r}
result_table( mtch, feasible_only = TRUE )
```

You can also get the final generated result as a data.frame by casting the result into a dataframe:
```{r}
head( as.data.frame( mtch ), n = 10 )
```

You can estimate impacts on the matched dataset using whatever tools you want, or use the options discussed in our paper as so:
```{r}
get_ATT_estimate( mtch )
```


# Dependencies

This package has some tricky dependencies.
In particular, it (optionally) uses a DGP (for simulation) from ACIC 2016:

```
remotes::install_github("vdorie/aciccomp/2016")
```

You should not need this package unless you are generating synthetic data.



